Bayesian Nonparametric System Reliability\\ using Sets of Priors

### 2016-01-04 ijar-npb-ms.tex
figure parameter sets

As was shown by \citet{2009:WalterAugustin}, %Walter \& Augustin (2009),
we can have both tractability and meaningful reaction to prior-data conflict
by using sets of priors $\MktZ$ produced by parameter sets $\PktZ = [\nktzl, \nktzu] \times [\yktzl, \yktzu]$. 
(A detailed discussion of different choices for $\PktZ$ is given in \citet[\S 3.1]{2013:diss-gw}.)
In our model, each prior parameter pair $(\nktz, \yktz) \in \PktZ$
corresponds to a Beta prior, thus $\MktZ$ is a set of Beta priors.
The set of posteriors $\MktN$ is obtained by updating each prior in $\MktZ$ according to Bayes' Rule.
This element-by-element updating may seem ad-hoc, but can be rigorously justified
as ensuring coherence \citep[\S 2.5]{1991:walley}, and was termed ``Generalized Bayes' Rule'' by \citet[\S 6.4]{1991:walley}.
Due to conjugacy, $\MktN$ is a set of Beta distributions with parameters $(\nktn, \yktn)$
obtained from updating $(\nktz, \yktz) \in \PktZ$ according to \eqref{eq:nyupdate},
and so can be described efficiently through the set of updated parameters
\begin{align*}
\PktN &= \Big\{ (\nktn, \yktn) \mid (\nktz, \yktz) \in \PktZ = [\nktzl, \nktzu] \times [\yktzl, \yktzu] \Big\}\,.
\end{align*}
Such rectangular prior parameter sets $\PktZ$ have been shown
to balance desirable model properties and ease of elicitation quite well.
%
For each component type $k$ and time point $t$,
one has to choose only the four parameters $\nktzl, \nktzu, \yktzl, \yktzu$
(so $4 \times |{\cal T}|$ parameters are needed to define the set of prior distributions characterizing
prior knowledge on the survival function of components of type $k$);
notwithstanding this, the model has favourable inference properties.

@@

In absence of prior-data conflict, 
$\PktN$ shrinks in the $\ykt$ dimension;
how much it shrinks depends on $\nktz \in [\nktzl, \nktzu]$,
leading to the so-called spotlight shape depicted in Figure***.
As $\yktn$ gives the posterior expectation for the functioning probability $p_t^k$,
shorter $\yktn$ intervals mean more precise knowledge about $p_t^k$.
Also, the variance interval for $p_t^k$ will decrease
as the Beta distributions in $\MktN$ will be more pointed
due to the increase of $\nktz$ to $\nktn$.

In case of prior-data conflict ($s^k_t/n_k \not\in [\yktzl, \yktzu]$),
$\PktN$ has instead the so-called banana shape,
arising from $\yktn$ intervals being shifted closer towards $s^k_t/n_k$
for lower $\nktn$ values than for higher $\nktn$ values, see Figure***.
Overall, this results in a wider $\yktn$ interval as compared to the non-conflict case, 
reflecting the extra uncertainty due to prior-data conflict,
thus making more cautious probability statements about $p_t^k$.

\td{Figure with $\PN$s and sets of beta cdfs for conflict and no conflict case.}

@@

With the structure defined and the individual components numbered, it 
just remains to specify the types of each component.  This can be done
using the \texttt{setCompTypes} function.  This function takes the
system graph and a list of component type names and corresponding
component numbers.  Thus, completing the example for Figure
\ref{fig:bridge-layout}:
\noindent\texttt{sys <- setCompTypes(sys, list("T1"=c(1), "T2"=c(6),}

>>>>

As was shown by \citet{2009:WalterAugustin}, %Walter \& Augustin (2009),
we can have both tractability and meaningful reaction to prior-data conflict
by using sets of priors $\MktZ$ produced by parameter sets $\PktZ = [\nktzl, \nktzu] \times [\yktzl, \yktzu]$. 
(A detailed discussion of different choices for $\PktZ$ is given in \citet[\S 3.1]{2013:diss-gw}.)
In our model, each prior parameter pair $(\nktz, \yktz) \in \PktZ$
corresponds to a Beta prior, thus $\MktZ$ is a set of Beta priors.
The set of posteriors $\MktN$ is obtained by updating each prior in $\MktZ$ according to Bayes' Rule.
This element-by-element updating may seem ad-hoc, but can be rigorously justified
as ensuring coherence \citep[\S 2.5]{1991:walley}, and was termed ``Generalized Bayes' Rule'' by \citet[\S 6.4]{1991:walley}.
Due to conjugacy, $\MktN$ is a set of Beta distributions with parameters $(\nktn, \yktn)$
obtained from updating $(\nktz, \yktz) \in \PktZ$ according to \eqref{eq:nyupdate},
and so can be described efficiently through the set of updated parameters
\begin{align*}
\PktN &= \Big\{ (\nktn, \yktn) \mid (\nktz, \yktz) \in \PktZ = [\nktzl, \nktzu] \times [\yktzl, \yktzu] \Big\}\,.
\end{align*}
Such rectangular prior parameter sets $\PktZ$ have been shown
to balance desirable model properties and ease of elicitation quite well
\citep[pp.~123f]{2013:diss-gw}; \citep{Troffaes2013a-short}.
%
For each component type $k$ and time point $t$,
one has to choose only the four parameters $\nktzl, \nktzu, \yktzl, \yktzu$
(so $4 \times |{\cal T}|$ parameters are needed to define the set of prior distributions characterizing
prior knowledge on the survival function of components of type $k$);
notwithstanding this, the model has favourable inference properties.

\begin{figure}
\includegraphics[width=\textwidth]{paramsets}
\caption{Prior parameter set $\PktZ = [1,8] \times [0.7,0.8]$ and posterior parameter set $\PktN$
for data $s^k_t/n_k = 12/16$ (left) and $s^k_t/n_k = 0/16$ (right).
For no-conflict data ($s^k_t/n_k \in [\yktzl,\yktzu]$), $\PktN$ has the `spotlight' shape (left);
in case of prior-data conflict ($s^k_t/n_k \not\in [\yktzl,\yktzu]$), $\PktN$ has the `banana' shape (right).}
\label{fig:paramsets}
\end{figure}

@@

In absence of prior-data conflict, 
$\PktN$ shrinks in the $\ykt$ dimension;
how much it shrinks depends on $\nktz \in [\nktzl, \nktzu]$,
leading to the so-called spotlight shape depicted in Figure~\ref{fig:paramsets} (left).
As $\yktn$ gives the posterior expectation for the functioning probability $p_t^k$,
shorter $\yktn$ intervals mean more precise knowledge about $p_t^k$.
Also, the variance interval for $p_t^k$ will decrease
as the Beta distributions in $\MktN$ will be more pointed
due to the increase of $\nktz$ to $\nktn$.

In case of prior-data conflict ($s^k_t/n_k \not\in [\yktzl, \yktzu]$),
$\PktN$ has instead the so-called banana shape,
arising from $\yktn$ intervals being shifted closer towards $s^k_t/n_k$
for lower $\nktn$ values than for higher $\nktn$ values, see Figure~\ref{fig:paramsets} (right).
Overall, this results in a wider $\yktn$ interval as compared to the non-conflict case, 
reflecting the extra uncertainty due to prior-data conflict,
thus making more cautious probability statements about $p_t^k$.

\td{Figure with sets of beta cdfs and beta-binom cmfs for conflict and no conflict case.}

@@

With the structure defined and the individual components numbered, it 
just remains to specify the types of each component.  This can be done
using the \texttt{setCompTypes} function.  This function takes the
system graph and a list of component type names and corresponding
component numbers.  Thus, completing the example for Figure
\ref{fig:bridge-layout}:

\noindent\texttt{sys <- setCompTypes(sys, list("T1"=c(1), "T2"=c(6),}
